env_and_copies_stats

### 2023-03-28 code/analysis_code/stats/uni_variate.qmd
edits to stats

```{r}
library(tidyverse)
library(here)
library(Hmisc) #For lag function
library(tidymodels) #For modeling
library(ggpmisc) #For R2 equation on graph
library(dotwhisker) #Fpr visualization
```

@@

```{r}
dust0<- read_csv(here("data", "processed_data","dust_master.csv")) #Different Dust attributes
data0<- read_csv(here("data", "processed_data", "tx_master.csv")) #Master Data
```

@@

## Blind Oso Site:

#### Add one day lag

@@

#### Create a linear model

@@

```{r}
aug_test_bo %>% ggplot(aes(copies_mL, .pred)) +
  geom_point() +
  stat_smooth(method = "lm")+
  stat_poly_eq(aes(x = lag, y = copies_mL),
               rr.digits = 4) +
  labs(title = "LM DustxCopies (BO+1)")
```

## Canals:

@@

#### Create a linear model

@@

@@

```{r}
aug_test_c2 %>% ggplot(aes(copies_mL, .pred)) +
  geom_point() +
  stat_smooth(method = "lm")+
  stat_poly_eq(aes(x = lag, y = copies_mL),
               rr.digits = 4) +
  labs(title = "LM DustxCopies (C2+2)")
```

#### Create a linear model

@@

```{r}
aug_test_rd %>% ggplot(aes(lag, copies_mL)) +
  geom_point() +
  stat_smooth(method = "lm")+
  stat_poly_eq(aes(x = lag, y = copies_mL),
               rr.digits = 4) +
  labs(title = "LM DustxCopies (RD+2)")
```

>>>>

```{r, include = FALSE}
library(tidyverse)
library(here)
library(Hmisc) #For lag function
library(tidymodels) #For modeling
library(ggpmisc) #For R2 equation on graph
library(dotwhisker) #Fpr visualization
```

@@

```{r, include = FALSE}
dust0<- read_csv(here("data", "processed_data","dust_master.csv")) #Different Dust attributes
data0<- read_csv(here("data", "processed_data", "tx_master.csv")) #Master Data
```

@@

# Blind Oso Site:

### Add one day lag

@@

```{r}
bo2 %>% ggplot(aes(x = lag, y = copies_mL)) +
  geom_point() +
  stat_smooth(method = "lm")+
  stat_poly_eq(aes(x = lag, y = copies_mL),
               rr.digits = 4) +
  labs(title = "LM DustxCopies (BO+1)")
```

### Create a linear model

@@

# Canals:

@@

```{r}
c22 %>% ggplot(aes(x = lag, y = copies_mL)) +
  geom_point() +
  stat_smooth(method = "lm")+
  stat_poly_eq(aes(x = lag, y = copies_mL),
               rr.digits = 4) +
  labs(title = "LM DustxCopies (C2+2)")
```

### Create a linear model

@@

### Add two day lag

@@

```{r}
rd2 %>% ggplot(aes(lag, copies_mL)) +
  geom_point() +
  stat_smooth(method = "lm")+
  stat_poly_eq(aes(x = lag, y = copies_mL),
               rr.digits = 4) +
  labs(title = "LM DustxCopies (RD+2)")
```

### Create a linear model

@@
